Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-08-02 Ben_Manuscripts/hdphmm/response_to_reviewers.tex

    %r1_comment1
    \item \textit{The manuscript by Coscia et al. analyzes diffusion and transport of solute molecules
    in a low water content lyotropic liquid crystal using a statistical model developed on the basis 
    of molecular dynamics simulations. The purpose of the statistical model is two-fold; first to 
    extrapolate computed MSDs to longer times to obtain diffusion coefficients, and second to attempt
    to gain increased physical insight on diffusion mechanisms. These issues are important in 
    highly-confined/low-water content nanoporous materials, in which diffusion occurs through complex
    mechanisms and over long timescales. The manuscript will most likely be of interest to the community
    interested in nanoporous materials for separations.}

    Author reply: We thank the reviewer for their thoughtful assessment of our work.

    %r1_comment2
    \item \textit {Unfortunately, because there is no comparison with alternative techniques, it is 
    very difficult to evaluate this new approach relative to previous work that has examined similar 
    issues. There exist numerous other methods for extrapolating MSDs to longer time, which the 
    authors have not discussed. One such method is the “trajectory-extending kinetic Monte Carlo” 
    (TEKMC) approach of Brown and coworkers see e.g. Macromolecules 2010, 43, 9210-9214, 
    Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
    %BJC: well Venkat Ganesan just relinquished his anonymity
    add a comprehensive discussion of how their approach compares to this and similar methods. The 
    paper would be significantly improved if the authors were to perform and present TEKMC results 
    for their system, so that one could better evaluate the performance of their proposed method.}

    Author reply: We thank the reviewer for bringing our attention to these other interesting 
    approaches. They certainly merit discussion as alternative approaches for estimating mean 
    squared displacements on long timescales. We have added some discussion of these methods to 
    the introduction.

    \begin{quote}
    A number of approaches have been explored to inexpensively extend the relatively short
    trajectories output by molecular simulations which exhibit complex diffusive behaviors
    onto much longer timescales. The trajectory extending kinetic Monte Carlo (TEKMC) approach
    divides a unit cell into a three dimensional grid and quantifies the transition 
    probabilities of particles that can move between each subdivision allowing one to generate
    stochastic trajectories that reach the diffusive regime~\cite{neyertz_trajectory-extending_2010}
    It is possible to parameterize TEKMC models with relatively short simulation trajectories 
    which facilitates systematic studies of small perturbations to material constituents.~\cite{hanson_computer_2012}
    In a related approach, dynamic bond percolation (DBP) theory can be used to quantify the
    rate of transition between sites in a dynamically disordered medium and long timescale
    behavior can be propagated using kinetic Monte Carlo simulations.~\cite{druger_dynamic_1983}
    Webb et al. extended this approach by defining sites based on the molecular details of 
    a polymer electrolyte system, thus allowing them to explain ion diffusivities predicted by
    the model in terms of chemically specific interactions.~\cite{webb_chemically_2015}
    \end{quote}

    We have also modified the first sentence of the paragraph that follows in order to maintain
    good flow.

    Original text:
    \begin{quote}
    We have already advanced our understanding of LLC monomer design in our previous work
    by building stochastic time series models based on the chemical intuition gained
    from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
    membrane.
    \end{quote}

    Modified text:
    \begin{quote}
    Based on the chemical intuition gained from our previous qualitative MD studies of 
    solute transport in an H\textsubscript{II} phase LLC membrane, we have contributed our
    own stochastic modeling approaches with goals similar to both TEKMC and DBP.
    \end{quote}

    We agree that a full comparison of our method to other methods for computing long timescale 
    diffusion such as TEKMC would be very interesting and instructive but feel it would be better 
    suited as a separate study where we could include a number of approaches, including perhaps
    recent approaches we have developed within our research group.~\cite{coscia_capturing_2020} We would also prefer to have
    sufficient time to appropriately implement the technique for our system. Although it seems a
    fairly straightforward approach to implement, it is not immediately clear how we could
    optimally adapt the methodology to a monoclinic unit cell with two dimensional order. 
%    the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
%    our system which uses a monoclinic unit cell and has 2 dimensional order.

    As stated by the reviewer, there are two goals of our work: to obtain long timescale MSDs and
    to understand mechanisms leading to diffusive behavior. TEKMC may be a suitable alternative 
    approach to obtaining our first goal, but it is not clear that it could give the same level
    of mechanistic insight that the HDP-AR-HMM offers. Although the work by Hanson et al.
    (J. Phys Chem. B, 2012, 116, 95-103) is able to provide physical insight into the effect of
    nanoparticles on diffusion of gaseous penetrants in a polystyrene polymer matrix, it does so
    by testing hypotheses motivated by observations of the diffusion constant (predicted by TEKMC)
    in response to different temperatures and nanoparticle concentrations. This is actually pretty
    in line with the type of analysis we performed in our initial LLC work where we used the
    mean squared displacement and the qualitative characteristic of the solute time series in
    order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
    with minimal human intervention and characterize them in detail using the HDP-AR-HMM while 
    \textit{simultaneously} providing a method to estimate diffusion constants.

@@

    %r1_comment3
    %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
    \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
    authors to better emphasize and discuss “new physical insight” and “chemical details”, and spend
    less time on methodology. For example pages 5-16 are all on methodology, yet it is not until 
    Figure 8 of the paper (page 26) that the authors give any description of what the LLC system 
    they are studying is actually composed of. Presumably the LLC is made up of self-assembled 
    monomers (in water) shown in Figure 8a). I would encourage the authors to describe their 
    system more concretely much earlier in the paper... there is also no information on system 
    size, box dimensions, etc.}

    Author reply: We thank the reviewer for encouraging us to include more physical insight and
    further details about our molecular simulations. Regarding physical insight, it is our 
    understanding that the scope of JPC has been expanded to welcome papers which focus on 
    methodology. We have studied the structure of and transport of solutes within this 
    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019} We feel strongly that our current work should 
    emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
    systems beyond our example system. We would prefer not to cut any methodological details, as
    this would hurt the paper's reproducibilty, and lengthening the paper by including additional
    physical insight may narrow the audience willing to dive in.

@@

    %BJC: probably could add a picture of the system. Or is it okay to just reference another
    % paper? I would probably use the same pic anyways or something very similar.

    We do agree that there are certain basic simulation details that we have neglected to 
    mention. Therefore we have made the following edits to section 2.1 of the methods:

    We added the highlight text to the first sentence of the section:
    \begin{quote}
      We studied transport of solutes in the H\textsubscript{II} phase using \hl{our
      previously developed} atomistic molecular model of four pores in a 
      \hl{$9.4\times9.4\times7.6$ nm} monoclinic unit cell with 10\% water by weight, 
      \hl{totaling 62,000 atoms}.    
    \end{quote}

    We have also added the following text describing the model: %BJC: not actually added yet
    \begin{quote}
    %BJC: this is verbatim from last response to reviewers so far
    We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
    We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
    solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
    assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
    GAFF is very commonly used in simulations with diverse organic chemical functionality, 
    and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
    water model. We chose these standard force fields and generalizable parameterization 
    approaches so that a range of solutes and monomers could be self-consistently and easily 
    studied. 
    %BJC: The following wasn't explicitly asked for, so I could omit    
    The main goal of this work is to develop stochastic models which can reproduce
    solute behavior on MD time scales, independent of the choice of force field. In future 
    work, it may be beneficial to employ specialized force fields, including polarizable 
    force fields or other higher-order effects in order to improve the accuracy of structure 
    parameters and selectivity predictions.
    \end{quote}

    %r1_comment4
    \item \textit{The authors should more clearly note that their discussion largely applies only 
    to very low water content LLC regimes (such as the 10\% LLC studied). For higher water content 
    LLCs (e.g. $>$ 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
    simulations. While the authors are surely well aware of this, the reader may not be, and it is
    important to clearly distinguish the regimes.}

    Author reply: We thank the reviewer for making this point. In higher water content systems, 
    the time scales necessary to reach a diffusive regime will be much more attainable with 
    standard MD. However, we do contend that our method would still be very useful for studying
    solute dynamics in these higher water content systems. Interactions characterized by different
    dynamical behavior even on short time scales can still be highly informative. This is the
    basis for the point we make in the introduction:``...direct calculations of diffusion 
    constants may obscure the molecular mechanisms controlling transport". Therefore we would
    prefer not to limit the range of application of this method. 
    %BJC: If it would be better to modify the text, then we could add something to the effect: If you only care about diffusivity, then this level of
    % modeling isn't necessary in many systems.

@@

    The generalization of this procedure to three dimensions will be under active investigation 
    in the near future. As mentioned, we are interested in applying this approach to bicontinuous
    cubic phases like the gyroid. Based on our current understanding, we would model solute dynamics
    in three dimensions and set the mean vector, $\mathbf{c}$ equal to $\mathbf{0}$. Of course, this
    may result in solutes exploring a three dimensional shape that does not share the geometric 
    features of the studied phase. Our hypothesis is that we can add one or more additional 
    dimensions to the time series passed to the HDP-AR-HMM that includes a distance from the pore centers. 
    We could define the pore center using a spline or a surface and transitions would likely
    favor moves towards states that exist closer to the pore interiors. Alternatively, it may prove
    necessary to constrain solute positions to the means in each dimension. However, this would require 
    much more data and would likely require us to explore less expensive models as described in
    the response to Reviewer 2 below.

    %BJC: figured I'd get your feedback on above before writing the part that will go into the text.

@@

    %r1_comment6
    \item \textit{As stated in the introduction, one motivation for the work is that “...one 
    cannot reliably compute diffusion constants because MSDs are often non-linear on the timescales
    accessible to molecular simulation”. Later on in section 2.4, the authors state “For the 
    purposes of our analysis, we assume ergodicity of the 24 solute trajectories.” These are 
    contradictory statements. If the trajectories are ergodic, then MSDs will be linear by 
    definition The authors should clarify. Similarly, in Figure 7, if the simulations are indeed 
    ergodic the red and blue bars should be proportional to each other.}

    Author reply: We thank the reviewer for identifying the potential confusion that could be
    caused by our use of the word 'ergodic'. Figure 7 clearly demonstrates that individual trajectories
    are not by themselves ergodic. Our intention was to communicate our assumption that collectively all 24 
    trajectories visit all possible dynamic states with representative probability. This is 
    necessary in order to make accurate long timescale predictions. The 5 $\mu s$ length of our 
    simulations was intended to increase the validity of this assumption.

    The use of the word `ergodic' is not necessary, therefore we have modified the text as follows
    to remove the source of potential miscommunication:

@@

    %r2_comment1
    \item \textit{This paper presents an approach to study transport mechanisms of solutes within
    membranes by applying the sticky hierarchical Dirichlet process autoregressive hidden Markov model
    (HDP-AR-HMM) to molecular dynamics simulation trajectories spanning long times (5 microseconds). 
    Using this method, the authors reveal different dynamic states associated with the transport of 
    solute across a membrane, and interpret them on the basis of solute-membrane interactions. The 
    paper is clear, well written, and relevant to the Journal of Physical Chemistry. I only have a 
    couple of suggestions and minor corrections:}

    Author reply: We thank the reviewer for their kind assessment of our work.

    %r2_comment2
    \item \textit{A motivation for the study is providing a computational tool to guide experimentalists
    in designing membrane materials. However, given the length of the molecular dynamics simulations 
    required, it is presumably impractical to carry a large-scale screening in this way. It would be 
    useful if the authors were more explicit about the role of this approach in guiding experiments, 
    and what would be its advantages and limitations compared to a purely experimental search.}

    Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
    method as a tool for experimentalists. In short, there are many ways we can envision that 
    would make this approach more amenable to high throughput simulations. The length of our 
    simulations in this paper are indeed quite long. The dynamics of the solutes are somewhat 
    slow and we wanted to ensure we gathered enough data for a sufficient parameterization. 
    Putting aside brute force high throughput simulations that could be enabled by the 
    ever-increasing availability of HPC resources, it would be to our benefit to use the system
    in this work as a benchmark to explore much less expensive models.
    %BJC: I'm not exactly sure where to put this. Originally I thought conclusions because it's
    %not really a method, but seemed to make the most sense near the system description.
    We propose some ideas to this end in the text we have added to the end of Section 2.1, where
    our simulations are described:
    \begin{quote}
    In consideration of our ultimate goal, which is to use high-throughput simulations to 
    facilitate our understanding of LLC membrane design for solute-specific separations, the size 
    of our system and length of the accompanying molecular simulations appears to be somewhat 
    impractical. We would like to emphasize that our large, fully atomistic models will be
    extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
    could explore systems built with fewer LLC monomers by making the membrane pores shorter. We 
    could also build systems with higher concentrations of solutes in order to gather more 
    dynamical data on shorter timescales. Using what we have learned about the radial distribution
    functions of these solutes in this and our previous work~\cite{coscia_chemically_2019}, it may be possible to 
    learn how to create initial configurations with solutes initially distributed in a way that
    is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
    accessible membrane structural space more quickly and reducing the amount of unequilibrated
    data that must be discarded. % could mention GCMC?
    Finally, it may be possible to speed up our simulations by 
    reducing the number of atoms using united-atom representations of the liquid crystal monomers.
    %BJC: How strong of an influence would hydrogen mass repartitioning have on hydrogen bonding?
    %, or by using hydrogen mass repartitioning to allow us to increase the MD time step.

@@

    %r2_comment3
    \item \textit{Have the authors attempted to compare their results directly to experimental data? 
    It would be useful to clarify whether the predicted selectivities are expected to be quantitatively
    accurate or just reflect trends.}

    %BJC: This is copied straight from the reviewer response for the previous paper.
    Author reply: The reviewer makes a valid point. This work started in parallel with experimental
    work which promised solute flux and selectivities that we could compare directly to our
	simulations. However, synthesizing an aligned hexagonal phase membrane has been a practical
	challenge for our experimental collaborators and much of their focus has shifted to 
	membranes formed by liquid crystals that self-assemble into bicontinuous cubic architectures
	which are much simpler to synthesize. We have also started to shift our focus towards models 
	of the bicontinuous cubic phase, which do have much more experimental data. However, our 
	research into generating physically accurate molecular models of that phase lags our work on
	time series modeling. In future work, we will be able to apply this technique to these 
	bicontinuous systems for which we have experimental data.

    %r2_comment4    
    \item \textit{As two very minor corrections, in page 15 line 8 it should say "Method 1", and in 
    page 17 line 5 the angle should be H-D-A.}

    % BJC: reviewer is right, VMD docs are misleading: https://www.ks.uiuc.edu/Research/vmd/plugins/hbonds/
    Author reply: We thank the reviewer for pointing out our potential errors. For the hydrogen bond
    criteria we have updated the text from ``D-H-A" to ``H-D-A". Regarding page 15 line 8 (``Method 2:
    Since trajectories generated by Method 2..."), changing ``Method 2" to ``Method 1" would actually be 
    incorrect. At the beginning of Section 2.4, we defined two techniques for generating stochastic 
    trajectories. ``Method 2'' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
    trajectory generation. This is a clear lack of clarity on the author's part and therefore we 
    have made an effort to modify our wording to avoid confusion.

### 2020-08-08 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Small edits
Started response to reviewers for hdphmm
Tweaks for final manuscript.

  The goal of this work is not to definitively determine which modeling
  approach is better but to evaluate their performance independently because
  they both have potential value dependent on a given research study's goals.
  The anomalous diffusion approach provides a systematic way to compare the
  dynamical behavior of different solutes based solely on the time series of 
  their center of mass positions. The process of choosing the correct anomlous
  diffusion modeling approach provides its own mechanistic insight since it 
  requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The Markov state-dependent
  dynamical model characterizes explicitly defined trapping mechanisms,
  providing a clear picture of solute behavior while in each trapped state as
  well as the equilibrium occupation of each trapping state.  It is possible to
  use the two modeling approaches in tandem, the anomalous diffusion approach to
  identify mechanisms, and the Markov state-dependent dynamical model to 
  characterize mechanisms.

@@

  \label{r1_comment2} % BJCR: description of force field.   
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which used TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD timescales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.

@@

  Despite relatively good predictions of the MD MSD, qualitative mismatch
  between stoachastic and MD simulated trajectories suggest that the Markov
  state-dependent dynamical model may be giving the right answers for the
  wrong reasons. We plotted typical realizations of the Markov state-dependent
  dynamical model for each solute and compared them to MD in 
  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
  or large hops. There are two reasons for this behavior. First, the width of
  hop length distributions are much smaller than those of the anomalous diffusion
  model. Closer examination of the characteristic MD trajectories shown in
  Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
  accumulation of a series of hops in the same direction. All of the hops generated
  by the Markov state-dependent dynamical model are negatively correlated which
  prevents this from happening. The second reason is a consequence of using a 
  single hop length distribution for transitions. This was necessary because we 
  could not collect enough data to fit all of the possible transition distributions
  and because we could not correlate emissions coming from different hop 
  distributions. Many transitions occur between two trapped states where the 
  transitional hops are actually very small. Our model ignores this physical 
  restriction which can cause the solute to drift rather than stay trapped.

@@

  The scaling of solute flux with pore length is primarily influenced by
  anti-correlation between solute hops. In Figure~\ref{fig:beta}a, we show that
  $\beta$ is inversely related to the Hurst parameter. This makes intuitive
  sense since higher degrees of anti-correlation should slow the rate at which
  solutes cross a membrane pore of a given length. When we remove anti-correlation between
  hops (set $H$=0.5), the length dependence becomes the same for all solutes,
  dropping to a value just below 2. This also implies that hop lengths and
  dwell times do not affect length dependence since each solute exhibits
  different hopping and trapping behavior yet are all parameterized by the same
  value of $\beta$ when $H$=0.5. We further verified this claim by removing
  hop anti-correlation and setting all dwell times equal to one timestep,
  effectively simulating Brownian motion.  The length dependence remains
  unchanged.

@@

  In a broader context, it is clear that time series modeling may be a useful way
  to form a clear connection between complex solute dynamics on the nanosecond 
  timescale and macroscopic observables. On the nanoscopic scale, one can both 
  learn and characterize dynamical modes in order to identify areas of potentially
  impactful molecular-level design changes. For example, it may be possible to 
  modify solute transport rates and selectivities in LLC membranes by redesigning 
  the LLC monomers to mitigate or enhance their chemically dependent interactions
  with different solutes. With these models, dynamics can be propagated onto much 
  longer time with computational ease. This allows one not only to predict a 
  macroscopic observable for a specific system, but to explicitly calculate the 
  effect of perturbations to model parameters that may result from a monomer 
  design change. Overall, we hope that this work can advance the reader's 
  understanding of how one can apply time series analysis in order to understand 
  complex diffusive behavior in any system of interest.

@@

% LocalWords:  solute MSDs solutes solute's LLC BJC nanoporous maginn Lyotropic
% LocalWords:  micropollutants LLCs amphiphilic mesophases feng Bicontinuous EG
% LocalWords:  permeability hatakeyama zhou resel selectivities Edisonian CTRW
% LocalWords:  subdiffusive timescale timescales subdiffusion FBM RWF metzler
% LocalWords:  jeon neusius pdf Sokolov ony MSD MSMs chodera MSM AcOH URE MeOH
% LocalWords:  Hbonding hbonds hbond GROMACS berendsen gromacs der spoel hess
% LocalWords:  wt Na GA carboxylate Parrinello Rahman barostat rescale msd dt
% LocalWords:  superdiffusive EB sFBM min Hurwitz factoid MLEs autocovariance
% LocalWords:  evy sFLM FLM sFLMcut Dirichlet saiid fbm Stoev Taqqu MLE TODO SI
% LocalWords:  vvvv wehmeyer MSMbuilder pyEMMA featurization Phys Chem bayesian
% LocalWords:  Markovianity MSDDMs MSDDM resampling TBD MSD's CTRWs GCL acf ACH
% LocalWords:  urea's alkane overlayed SFLMcut underpredicted Gaussians HMM PRF
% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC QI
% LocalWords:  RMACC TOC Nanoscale Coscia lyotropic morphologies HII geens MFPT
% LocalWords:  darvishmanesh bouchaud integrator LINCS clauset sFBMcut pyemma
% LocalWords:  msmbuilder diffusivity Eq vt dz erfc permeabilities Kedem zoubi
% LocalWords:  Katchalsky's nanofiltration ultrafiltration trans convective py
% LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
% LocalWords:  timestep pre selectivtiy foulants subfigures RWFs roman github
% LocalWords:  al linkable nanopores klages

>>>>

  The goal of this work is not to definitively determine which modeling
  approach is better but to evaluate their performance independently because
  they both have potential value dependent on a given research study's goals.
  The anomalous diffusion approach provides a systematic way to compare the
  dynamical behavior of different solutes based solely on the time series of 
  their center of mass positions. The process of choosing the correct anomalous
  diffusion modeling approach provides its own mechanistic insight since it 
  requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The Markov state-dependent
  dynamical model characterizes explicitly defined trapping mechanisms,
  providing a clear picture of solute behavior while in each trapped state as
  well as the equilibrium occupation of each trapping state.  It is possible to
  use the two modeling approaches in tandem, the anomalous diffusion approach to
  identify mechanisms, and the Markov state-dependent dynamical model to 
  characterize mechanisms.

@@

  \label{r1_comment2} % BJCR: description of force field.   
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD timescales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.

@@

  Despite relatively good predictions of the MD MSD, qualitative mismatch
  between stochastic and MD simulated trajectories suggest that the Markov
  state-dependent dynamical model may be giving the right answers for the
  wrong reasons. We plotted typical realizations of the Markov state-dependent
  dynamical model for each solute and compared them to MD in 
  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
  or large hops. There are two reasons for this behavior. First, the width of
  hop length distributions are much smaller than those of the anomalous diffusion
  model. Closer examination of the characteristic MD trajectories shown in
  Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
  accumulation of a series of hops in the same direction. All of the hops generated
  by the Markov state-dependent dynamical model are negatively correlated which
  prevents this from happening. The second reason is a consequence of using a 
  single hop length distribution for transitions. This was necessary because we 
  could not collect enough data to fit all of the possible transition distributions
  and because we could not correlate emissions coming from different hop 
  distributions. Many transitions occur between two trapped states where the 
  transitional hops are actually very small. Our model ignores this physical 
  restriction which can cause the solute to drift rather than stay trapped.

@@

  The scaling of solute flux with pore length is primarily influenced by
  anti-correlation between solute hops. In Figure~\ref{fig:beta}a, we show that
  $\beta$ is inversely related to the Hurst parameter. This makes intuitive
  sense since higher degrees of anti-correlation should slow the rate at which
  solutes cross a membrane pore of a given length. When we remove anti-correlation between
  hops (set $H$=0.5), the length dependence becomes the same for all solutes,
  dropping to a value just below 2. This also implies that hop lengths and
  dwell times do not affect length dependence since each solute exhibits
  different hopping and trapping behavior yet are all parameterized by the same
  value of $\beta$ when $H$=0.5. We further verified this claim by removing
  hop anti-correlation and setting all dwell times equal to one time step,
  effectively simulating Brownian motion.  The length dependence remains
  unchanged.

@@

  In a broader context, it is clear that time series modeling may be a useful way
  to form a clear connection between complex solute dynamics on the nanosecond 
  timescale and macroscopic observables. On the nanoscale, one can both 
  learn and characterize dynamical modes in order to identify areas of potentially
  impactful molecular-level design changes. For example, it may be possible to 
  modify solute transport rates and selectivities in LLC membranes by redesigning 
  the LLC monomers to mitigate or enhance their chemically dependent interactions
  with different solutes. With these models, dynamics can be propagated onto much 
  longer time with computational ease. This allows one not only to predict a 
  macroscopic observable for a specific system, but to explicitly calculate the 
  effect of perturbations to model parameters that may result from a monomer 
  design change. Overall, we hope that this work can advance the reader's 
  understanding of how one can apply time series analysis in order to understand 
  complex diffusive behavior in any system of interest.

@@

% LocalWords:  solute MSDs solutes solute's LLC BJC nanoporous maginn Lyotropic
% LocalWords:  micropollutants LLCs amphiphilic mesophases feng Bicontinuous EG
% LocalWords:  permeability hatakeyama zhou resel selectivities Edisonian CTRW
% LocalWords:  subdiffusive timescale timescales subdiffusion FBM RWF metzler
% LocalWords:  jeon neusius pdf Sokolov ony MSD MSMs chodera MSM AcOH URE MeOH
% LocalWords:  Hbonding hbonds hbond GROMACS berendsen gromacs der spoel hess
% LocalWords:  wt Na GA carboxylate Parrinello Rahman barostat rescale msd dt
% LocalWords:  superdiffusive EB sFBM min Hurwitz factoid MLEs autocovariance
% LocalWords:  evy sFLM FLM sFLMcut Dirichlet saiid fbm Stoev Taqqu MLE TODO SI
% LocalWords:  vvvv wehmeyer MSMbuilder pyEMMA featurization Phys Chem bayesian
% LocalWords:  Markovianity MSDDMs MSDDM resampling TBD MSD's CTRWs GCL acf ACH
% LocalWords:  urea's alkane overlayed SFLMcut underpredicted Gaussians HMM PRF
% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC QI
% LocalWords:  RMACC TOC Nanoscale Coscia lyotropic morphologies HII geens MFPT
% LocalWords:  darvishmanesh bouchaud integrator LINCS clauset sFBMcut pyemma
% LocalWords:  msmbuilder diffusivity Eq vt dz erfc permeabilities Kedem zoubi
% LocalWords:  Katchalsky's nanofiltration ultrafiltration trans convective py
% LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
% LocalWords:  time step pre selectivtiy foulants subfigures RWFs roman github
% LocalWords:  al linkable nanopores klages BJCR BJCB MRSB BJCA BJCC
% LocalWords:  Donnan steric Antechamber polarizable intramolecular
% LocalWords:  quasiharmonic ester decorrelated nanoscale
% LocalWords:  nanoscopic impactful
